### 2010-02-02 doc/manuals/configuration/configuration_manual.tex
Few words about GSI MCC. Small enhancements.

\subsubsection{TCP MCC}\label{sec:tcp-mcc}
The TCP message component is named \texttt{tcp.service} and should be the first
component in a chain. It is used to setup a server socket which will listen for
incoming connections. The socket can be configured using the \texttt{Listen}
element, which can occur multiple times and under each element the following
child elements can be specified:
\begin{description}
\item[\texttt{Interface}] This element specifies the interface which socket
  should listen on. If this element is not specified then the socket will listen
  on all available interfaces.
\item[\texttt{Port}] The port which the socket should bind to should be
  specified with this element. If no port is specified an error will be reported
  and this \texttt{Listen} element will be ignored.
\item[\texttt{Version}] The IP version can be specified by this element, and by
  default both version 4 and 6 will be used. It is possible to specify version 4
  or 6 only.
\item[\texttt{NoDelay}] By default Nagle's algorithm is used for sending data,
  however if the \texttt{NoDelay} element is set to \texttt{true} data will be
  send when ready.
\item[\texttt{Timeout}] Specifies how much time, in seconds, there should be
  used on waiting for a client response. If no client response is obtained
  before timeout the connection is dropped. The default value is 60 seconds.
\end{description}
It is also possible to put a limit on incoming connections, and how these should
be handled if the limit is reached. The limit can only be put on all configured
interfaces, and not per interface. The \texttt{Limit} element specifies the
limit on incoming connections, and the \texttt{drop} attribute specifies whether
new connections, above the limit, will be put on hold (default) or if they
should be dropped, which is specified by setting the attribute to \texttt{true}.

@@

\subsubsection{TLS MCC}\label{sec:tls-mcc}
A security layer can be configured with the TLS MCC, named \texttt{tls.service},
and it should be put on top of a TCP MCC. By default it is able to understand
the SSLv2, SSLv3 and TLSv1 protocols, however the \texttt{Handshake} element can
be used to specify another behaviour. The supported values for the
\texttt{Handshake} element are \texttt{TLS} (default) and \texttt{SSLv3}, where
specifying the latter will configure a MCC which only understand the SSLv3
protocol. If other values than the mentioned ones are given, then \texttt{TLS}
will be used.

@@

%~ \paragraph{Globus Policy}
%~ attribute \texttt{PolicyGlobus} (CACertificatePath).
%~
%~ \paragraph{Trusted VOMS Credentials}
%~ \texttt{VOMSCertTrustDNChain}
%~ <xsd:sequence>
  %~ \texttt{VOMSCertTrustDN}
  %~ \texttt{VOMSCertTrustRegex}
%~ </xsd:sequence>
%~ The DN list of the trusted voms server credential;
%~ in the AC part of voms proxy certificate, voms proxy
%~ certificate comes with the server certificate which is
%~ used to sign the AC. So when verifying the AC on the
%~ AC-consuming side (in ARC1, it is the MCCTLS which will
%~ consumes the AC), the server certificate will be checked
%~ against a trusted DN list. Only if the DN and issuer's
%~ DN of server certificate exactly matches the DN list
%~ in the configuration under TLS component, the AC can be trusted
%~
%~ \texttt{VOMSCertTrustDNChainsLocation}
%~ DN list in an external file, which is in the same format as VOMSCertTrustDNChain
%~
%~ \begin{lstlisting}[language=xml]
%~ ...
%~ <Component name="tls.service" id="tls">
  %~ <VOMSCertTrustDNChain>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustRegex></VOMSCertTrustRegex>
  %~ </VOMSCertTrustDNChain>
%~ </Component>
%~ ...
%~ \end{lstlisting}

@@

%~ \subsubsection{GSI MCC}\label{sec:gsi-mcc}
%~ \texttt{KeyPath} Location of private key.
%~
%~ \texttt{CertificatePath} Location of public certificate.
%~
%~ \texttt{ProxyPath} Location of proxy credentials - includes certificates, key
%~ and chain of involved certificates. Overwrites elements \texttt{KeyPath} and
%~ \texttt{CertificatePath}.

@@

\subsection{Security Handlers}\label{sec:Security Handlers}
\subsubsection{Identity Mapping}% identity.map
\subsubsection{ARC Authorization}% arc.authz
\subsubsection{Delegation Collector}% delegation.collector
\subsubsection{Username Token}% usernametoken.handler
%\subsubsection{Delegation Handler}% delegation.handler
%\subsubsection{X509 Token}% x509token.handler
%\subsubsection{SAML Token}% samltoken.handler
%\subsubsection{SAML Single Sign-On}% saml2ssoassertionconsumer.handler

>>>>

\subsubsection{TCP MCC}\label{sec:tcp-mcc}
The TCP message component is named \texttt{tcp.service} and should be the first
component in a chain. It is used to setup a server socket which will listen for
incoming connections. The socket can be configured using the \texttt{Listen}
element, which can occur multiple times and under each element the following
child elements can be specified:
\begin{description}
\item[\texttt{Interface}] This element specifies the interface which socket
  should listen on. If this element is not specified then the socket will listen
  on all available interfaces.
\item[\texttt{Port}] The port which the socket should bind to should be
  specified with this element. If no port is specified an error will be reported
  and this \texttt{Listen} element will be ignored.
\item[\texttt{Version}] The IP version can be specified by this element, and by
  default both version 4 and 6 will be used. It is possible to specify version 4
  or 6 only.
\item[\texttt{NoDelay}] By default Nagle's algorithm is used for sending data,
  however if the \texttt{NoDelay} element is set to \texttt{true} data will be
  sent when ready. This is mainly used for optimizing connections for communication
  patterns which involve a lot of very short messages exchanged by service 
  and client.
\item[\texttt{Timeout}] Specifies how much time, in seconds, data sending or
  receiving may take. If time is exceeded MCC reports error and in most cases 
  connection is dropped. The default value is 60 seconds.
\end{description}
It is also possible to put a limit on number of incoming connections, and how 
these should be handled if the limit is reached. The limit can only be put on all 
configured interfaces, and not per interface. The \texttt{Limit} element specifies 
the limit on incoming connections, and the \texttt{drop} attribute specifies whether 
new connections, above the limit, will be put on hold (default) or if they should 
be dropped, which is specified by setting the attribute to \texttt{true}.

@@

\subsubsection{TLS MCC}\label{sec:tls-mcc}
A security layer can be configured with the TLS MCC, named \texttt{tls.service},
and it should be put on top of a TCP MCC. By default it is able to understand
the SSLv2 (hadshake only), SSLv3 and TLSv1 protocols, however the \texttt{Handshake} 
element can be used to specify another behaviour. The supported values for the
\texttt{Handshake} element are \texttt{TLS} (default) and \texttt{SSLv3}, where
specifying the latter will configure a MCC which only understand the SSLv3
protocol. If other values than the mentioned ones are given, then \texttt{TLS}
will be used.

@@

If element \texttt{CACertificatesDir} have attribute \texttt{PolicyGlobus} set
to "true" additional verification of client credentials is performed. Client
credentials are restricted to be signed by specific Certification Authorities
as specified in additional configuration files. Those files are stored in the
location specified by the element \texttt{CACertificatesDir} and have names
made of the hash of the subject of CA certificate followed by \texttt{.signing\_policy}
suffix. Information about format of those files may be found at 
http://dev.globus.org/wiki/Signing\_Policy.
%~
%~ \paragraph{Trusted VOMS Credentials}
%~ \texttt{VOMSCertTrustDNChain}
%~ <xsd:sequence>
  %~ \texttt{VOMSCertTrustDN}
  %~ \texttt{VOMSCertTrustRegex}
%~ </xsd:sequence>
%~ The DN list of the trusted voms server credential;
%~ in the AC part of voms proxy certificate, voms proxy
%~ certificate comes with the server certificate which is
%~ used to sign the AC. So when verifying the AC on the
%~ AC-consuming side (in ARC1, it is the MCCTLS which will
%~ consumes the AC), the server certificate will be checked
%~ against a trusted DN list. Only if the DN and issuer's
%~ DN of server certificate exactly matches the DN list
%~ in the configuration under TLS component, the AC can be trusted
%~
%~ \texttt{VOMSCertTrustDNChainsLocation}
%~ DN list in an external file, which is in the same format as VOMSCertTrustDNChain
%~
%~ \begin{lstlisting}[language=xml]
%~ ...
%~ <Component name="tls.service" id="tls">
  %~ <VOMSCertTrustDNChain>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustRegex></VOMSCertTrustRegex>
  %~ </VOMSCertTrustDNChain>
%~ </Component>
%~ ...
%~ \end{lstlisting}

\subsubsection{GSI MCC}\label{sec:gsi-mcc}
At its purpose MCC is similar to TLS described in section \ref{sec:tls-mcc}. It 
provides security layer using Globus implementation of GSS-API and corresponding 
communication protocol.

Its configuration element \texttt{KeyPath} and \texttt{CertificatePath} are 
identical to those of TLS MCC. This MCC is implemented using libraries of 
Globus Toolkit and its functionality and requirements are better to be 
described by descrition of Globus gssapi library.

Use of this MCC is not recommended due to non-standard origin of underlying
protocol.

@@

@@

\subsection{Security Handlers}\label{sec:Security Handlers}
\subsubsection{Identity Mapping}\label{sec:identitymap-shc}
\subsubsection{ARC Authorization}\label{sec:arcautz-shc}
\subsubsection{Delegation Collector}\label{sec:delegcollector-shc}
\subsubsection{Delegation Handler}\label{sec:deleghandler-shc}
\subsubsection{Username Token}\label{sec:unametoken-shc}
\subsubsection{Username Token}\label{sec:x509token-shc}
%\subsubsection{SAML Token}% samltoken.handler
%\subsubsection{SAML Single Sign-On}% saml2ssoassertionconsumer.handler

\subsection{Policy Decision Points}\label{sec:Policy Decision Points}
